Geometric models reveal the hidden structure of conceptual knowledge

### 2023-01-20 paper/main.tex
fixed error in reported numbers of questions (thanks for the catch PF!)

We hand-selected two roughly 10-minute course videos from the Khan Academy
platform: \textit{The Four Fundamental Forces} (an introduction to gravity,
electromagnetism, the weak nuclear force, and the strong nuclear force;
duration: 10 minutes and 29 seconds) and \textit{Birth of Stars} (an
introduction to how stars are formed; duration: 7 minutes and 57 seconds). We
hand-wrote 30 multiple choice questions: 10 about the conceptual content of
\textit{The Four Fundamental Forces}, another 10 about the conceptual content
of \textit{Birth of Stars}, and 10 other questions that tested for general
conceptual knowledge about basic physics (covering material that was not
presented in either video). The full set of questions may be found in
Table~\questions.

@@

\caption{\textbf{Experimental paradigm.} Participants alternate between
answering 10-question multiple choice quizzes and watching two Khan academy
videos. Each quiz contains a mix of 10 questions about each of: lecture 1,
lecture 2, and general physics knowledge. The specific questions reflected on
each quiz, and the orders of each quiz's questions, are randomized across
participants.}

>>>>

We hand-selected two roughly 10-minute course videos from the Khan Academy
platform: \textit{The Four Fundamental Forces} (an introduction to gravity,
electromagnetism, the weak nuclear force, and the strong nuclear force;
duration: 10 minutes and 29 seconds) and \textit{Birth of Stars} (an
introduction to how stars are formed; duration: 7 minutes and 57 seconds). We
hand-wrote 39 multiple choice questions: 15 about the conceptual content of
\textit{The Four Fundamental Forces}, another 15 about the conceptual content
of \textit{Birth of Stars}, and 9 other questions that tested for general
conceptual knowledge about basic physics (covering material that was not
presented in either video). The full set of questions may be found in
Table~\questions.

@@

\caption{\textbf{Experimental paradigm.} Participants alternate between
answering 13-question multiple choice quizzes and watching two Khan academy
videos. Each quiz contains a mix of 5 questions about lecture 1, 5 questions about lecture 2,
and 3 general physics knowledge questions. The specific questions reflected on
each quiz, and the orders of each quiz's questions, were randomized across
participants.}
